---
title: "Project3_Group_18"
author: "Rahasya Chandan and Tanamaye Poojari"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r}
library(dplyr)
library(magrittr)
library(stringr)
library(janitor)
library(reshape)
library(tibble)
library(ggplot2)
library(igraph)
library(ggraph)
library(tidyr)
library(readxl)
library(tidytext)
library(tidyverse)
library(tm)
```
Task 1

1. Reading and Cleaning Datasets
```{r}
#reading csv 
df_Keyword_data<-read.csv("https://raw.githubusercontent.com/rahasyac/keyword-network-analysis/main/Data/Keyword_data%20-%20Keyword_data.csv",na.strings = "")
#removing the unnecessary and empty rows
df_Keyword_data<-df_Keyword_data[-c(1,2,11,12,13,23,24,25,34,35,36,45,46,47,56,57,58),]
```
2. Extracting keyword data
```{r}
#finding unique keywords using stack
stacked_keywords<-stack(df_Keyword_data[,2:13])
#finding unique keywords in stacked words
unique_keywords<-sort(unique(stacked_keywords$values))
unique_keywords<-unique_keywords[c(-1)]
```
3. Read the adjacency matrix and convert it into a weighted network
```{r, include=FALSE}
#Weighted adjacency matrix 
answer<-matrix(0, nrow=length(unique_keywords), ncol=length(unique_keywords))
colnames(answer)<-unique_keywords
rownames(answer)<-unique_keywords


# creating weighted matrix
for(i in 1:length(df_Keyword_data$Keyword.2)){
  temp_row<-unlist(df_Keyword_data[i,])
  print(i)
  print(temp_row)
  temp_row<-temp_row[!is.na(temp_row)]
  keywords_list<-combn(temp_row,2)
  for(j in 1:length(keywords_list[1,])){
    rowind<-which(rownames(answer)==(keywords_list[1,j]))
    colind<-which(colnames(answer)==(keywords_list[2,j]))
    answer[rowind,colind]<-answer[rowind,colind]+1
    answer[colind,rowind]<-answer[colind,rowind]+1
  }
}

network<-graph_from_adjacency_matrix(answer,mode="undirected",weighted = TRUE)
weighted_network <- get.data.frame(network)
```
4. Compute node degree and strength
```{r}
#Compute node degree
node_degree<-degree(network,mode="all")

head(node_degree)
```
```{r}
#Compute node strength
node_strength<-strength(network)

head(node_strength)
```
5. Show the top 10 nodes by degree and top 10 nodes by strength
```{r}
#top 10 top 10 nodes by degree
sorted_node_degree <- sort(node_degree,decreasing = TRUE)
head(sorted_node_degree,10)
```
```{r}
#top 10 nodes by strength
sorted_node_strength <- sort(node_strength,decreasing = TRUE)
head(sorted_node_strength,10)
```
6. Show the top 10 node pairs by weight
```{r}
#Show the top 10 node pairs by weight
sorted_weights <- weighted_network[order(-weighted_network$weight),] 
head(sorted_weights,10)
```
7. Plot average strength on y-axis and degree on x-axis
```{r}
#Plot strength on y-axis and degree on x-axis
plot(node_degree,node_strength, main = "Strength Vs Degree",
     xlab = "Node Degree", ylab = "Node Strength",
     pch = 19, frame = FALSE)
```

Task 2

Reading and Cleaning Datasets
```{r}
#reading datasets from 2017-2022
dt2017 <- read_csv("https://raw.githubusercontent.com/rahasyac/word-frequency-analysis/main/elon/2017.csv")
dt2018 <- read_csv("https://raw.githubusercontent.com/rahasyac/word-frequency-analysis/main/elon/2018.csv")
dt2019 <- read_csv("https://raw.githubusercontent.com/rahasyac/word-frequency-analysis/main/elon/2019.csv")
dt2020 <- read_csv("https://raw.githubusercontent.com/rahasyac/word-frequency-analysis/main/elon/2020.csv")
dt2021 <- read_csv("https://raw.githubusercontent.com/rahasyac/word-frequency-analysis/main/elon/2021.csv")
dt2022 <- read_csv("https://raw.githubusercontent.com/rahasyac/word-frequency-analysis/main/elon/2022.csv")

df.list <- list(dt2017, dt2018, dt2019, dt2020, dt2021, dt2022)

wrangle <- function(x){
  x$tweet <-  gsub("@\\w+", "", x$tweet)
  x$tweet <- gsub("(f|ht)tp\\S+\\s*", "", x$tweet)
  x$tweet <-  gsub("[[:punct:]]", "", x$tweet)
  x$tweet <- trimws(x$tweet, which = c("both","left","right"), whitespace = "[\t\r\n]")
}

dt2017 <- data.frame(wrangle(dt2017))
dt2018 <- data.frame(wrangle(dt2018))
dt2019 <- data.frame(wrangle(dt2019))
dt2020 <- data.frame(wrangle(dt2020))
dt2021 <- data.frame(wrangle(dt2021))
dt2022 <- data.frame(wrangle(dt2022))

#Stop Words Dataframe
stopwords <- data.frame(word = stopwords(kind = "en"))
```
1. Compute word frequencies for each year. Exclude the stop words
```{r}
# Counting frequency of words for 2017
y2017 <- dt2017 %>%
          unnest_tokens(word, wrangle.dt2017.) %>%
          anti_join(stopwords)

freq2017 <- y2017 %>% count(word) %>% arrange(desc(n))
head(freq2017)

# Counting frequency of words for 2018
y2018 <- dt2018 %>% 
          unnest_tokens(word, wrangle.dt2018.) %>% 
          anti_join(stopwords)

freq2018 <- y2018 %>% count(word) %>% arrange(desc(n))
head(freq2018)

# Counting frequency of words for 2019
y2019 <- dt2019 %>% 
          unnest_tokens(word, wrangle.dt2019.) %>% 
          anti_join(stopwords)

freq2019 <- y2019 %>% count(word) %>% arrange(desc(n))
head(freq2019)


# Counting frequency of words for 2020
y2020 <- dt2020 %>% 
          unnest_tokens(word, wrangle.dt2020.) %>% 
          anti_join(stopwords)

freq2020 <- y2020 %>% count(word) %>% arrange(desc(n))
head(freq2020)

# Counting frequency of words for 2021
y2021 <- dt2021 %>% 
          unnest_tokens(word, wrangle.dt2021.) %>% 
          anti_join(stopwords)

freq2021 <- y2021 %>% count(word) %>% arrange(desc(n))
head(freq2021)

# Counting frequency of words for 2022
y2022 <- dt2022 %>% 
          unnest_tokens(word, wrangle.dt2022.) %>% 
          anti_join(stopwords)

freq2022 <- y2022 %>% count(word) %>% arrange(desc(n))
head(freq2022)
```

2.Showing top 10 words (for each year) by the highest value of word frequency
```{r}
#For 2017
topten2017 <- head(freq2017, 10)
topten2017

#For 2018
topten2018 <- head(freq2018, 10)
topten2018

#For 2019
topten2019 <- head(freq2019, 10)
topten2019

#For 2020
topten2020 <- head(freq2020, 10)
topten2020

#For 2021
topten2021 <- head(freq2021, 10)
topten2021

#For 2022
topten2022 <- head(freq2022, 10)
topten2022
```

3.Plotting histogram of word frequencies for each year
```{r}
#For 2017
ggplot(topten2017, aes(x = reorder(word, -n), y = n, fill = word)) + geom_col() +
  labs(title = "Word Frequency for 2017", x = "Word", y = "Frequency") 

#For 2018
ggplot(topten2018, aes(x = reorder(word, -n), y = n, fill = word)) + geom_col() +
  labs(title = "Word Frequency for 2018", x = "Word", y = "Frequency")

#For 2019
ggplot(topten2019, aes(x = reorder(word, -n), y = n, fill = word)) + geom_col() +
  labs(title = "Word Frequency for 2019", x = "Word", y = "Frequency")

#For 2020
ggplot(topten2020, aes(x = reorder(word, -n), y = n, fill = word)) + geom_col() +
  labs(title = "Word Frequency for 2020", x = "Word", y = "Frequency")

#For 2021
ggplot(topten2021, aes(x = reorder(word, -n), y = n, fill = word)) + geom_col() +
  labs(title = "Word Frequency for 2021", x = "Word", y = "Frequency")

#For 2022
ggplot(topten2022, aes(x = reorder(word, -n), y = n, fill = word)) + geom_col() +
  labs(title = "Word Frequency for 2022", x = "Word", y = "Frequency")
```

4.Using Zipf’s law and plot log-log plots of word frequencies and rank for each year
```{r}
freq2017$year <- 2017
freq2018$year <- 2018
freq2019$year <- 2019
freq2020$year <- 2020
freq2021$year <- 2021
freq2022$year <- 2022

# Finding Frequency by Rank for year 2017
t2017 <- freq2017 %>%
  group_by(year) %>%
  summarize(total = sum(n))
freq2017 <- left_join(freq2017, t2017)
freqrank2017 <- freq2017 %>%
  group_by(year) %>%
  mutate(rank = row_number(), `term frequency` = n / total) %>%
  ungroup()

rank_subset <- freqrank2017 %>%
  filter(
    rank < 500,
    rank > 10
  )

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

# Zipf Law Plot
freqrank2017 %>%
  ggplot(aes(rank, `term frequency`, color = year)) +
  labs(title = "Log-Log plot for 2017", x = "Rank", y = "Term Frequency") +
  geom_abline(intercept = -1.5634, slope = -0.6787,
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) +
  scale_x_log10() +
  scale_y_log10()


# Finding Frequency by Rank for year 2018
t2018 <- freq2018 %>%
  group_by(year) %>%
  summarize(total = sum(n))
freq2018 <- left_join(freq2018, t2018)
freqrank2018 <- freq2018 %>%
  group_by(year) %>%
  mutate(rank = row_number(), `term frequency` = n / total) %>%
  ungroup()
rank_subset <- freqrank2018 %>%
  filter(
    rank < 500,
    rank > 10
  )

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

freqrank2018 %>%
  ggplot(aes(rank, `term frequency`, color = year)) +
  labs(title = "Log-Log plot for 2018", x = "Rank", y = "Term Frequency") +
  geom_abline(intercept = -1.5802, slope = -0.6723,
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) +
  scale_x_log10() +
  scale_y_log10()


# Finding Frequency by Rank for year 2019
t2019 <- freq2019 %>%
  group_by(year) %>%
  summarize(total = sum(n))
freq2019 <- left_join(freq2019, t2019)
freqrank2019 <- freq2019 %>%
  group_by(year) %>%
  mutate(rank = row_number(), `term frequency` = n / total) %>%
  ungroup()
rank_subset <- freqrank2019 %>%
  filter(
    rank < 500,
    rank > 10
  )

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

# Zipf Law Plot
freqrank2019 %>%
  ggplot(aes(rank, `term frequency`, color = year)) +
  labs(title = "Log-Log plot for 2019", x = "Rank", y = "Term Frequency") +
  geom_abline(intercept = -1.5943, slope = -0.6711,
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) +
  scale_x_log10() +
  scale_y_log10()


# Finding Frequency by Rank for year 2020
t2020 <- freq2020 %>%
  group_by(year) %>%
  summarize(total = sum(n))
freq2020 <- left_join(freq2020, t2020)
freqrank2020 <- freq2020 %>%
  group_by(year) %>%
  mutate(rank = row_number(), `term frequency` = n / total) %>%
  ungroup()
rank_subset <- freqrank2020 %>%
  filter(
    rank < 500,
    rank > 10
  )

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

# Zipf Law Plot
freqrank2020 %>%
  ggplot(aes(rank, `term frequency`, color = year)) +
  labs(title = "Log-Log plot for 2020", x = "Rank", y = "Term Frequency") +
  geom_abline(intercept = -1.5991, slope = -0.6702,
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) +
  scale_x_log10() +
  scale_y_log10()


# Finding Frequency by Rank for year 2021
t2021 <- freq2021 %>%
  group_by(year) %>%
  summarize(total = sum(n))
freq2021 <- left_join(freq2021, t2021)
freqrank2021 <- freq2021 %>%
  group_by(year) %>%
  mutate(rank = row_number(), `term frequency` = n / total) %>%
  ungroup()
rank_subset <- freqrank2021 %>%
  filter(
    rank < 500,
    rank > 10
  )

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

# Zipf Law Plot
freqrank2021 %>%
  ggplot(aes(rank, `term frequency`, color = year)) +
  labs(title = "Log-Log plot for 2021", x = "Rank", y = "Term Frequency") +
  geom_abline(intercept = -1.6323, slope = -0.6532,
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) +
  scale_x_log10() +
  scale_y_log10()

# Finding Frequency by Rank for year 2022
t2022 <- freq2022 %>%
  group_by(year) %>%
  summarize(total = sum(n))
freq2022 <- left_join(freq2022, t2022)
freqrank2022 <- freq2022 %>%
  group_by(year) %>%
  mutate(rank = row_number(), `term frequency` = n / total) %>%
  ungroup()
rank_subset <- freqrank2022 %>%
  filter(
    rank < 500,
    rank > 10
  )

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

# Zipf Law Plot
freqrank2022 %>%
  ggplot(aes(rank, `term frequency`, color = year)) +
  labs(title = "Log-Log plot for 2022", x = "Rank", y = "Term Frequency") +
  geom_abline(intercept = -1.6323, slope = -0.6532,
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) +
  scale_x_log10() +
  scale_y_log10()

```

5. Creating Bigram Network Graphs for each year
```{r, results='hide'}
# For year 2017 
dt2017_bigrams <- dt2017 %>%
  unnest_tokens(bigram, wrangle.dt2017., token = "ngrams", n = 2)


# Counting the bigrams
dt2017_bigrams %>%
  count(bigram, sort = TRUE)

dt2017_bigrams_separated <- dt2017_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

dt2017_bigrams_filtered <- dt2017_bigrams_separated %>%
  filter(!word1 %in% stopwords$word) %>%
  filter(!word2 %in% stopwords$word)

dt2017_bigrams_counts <- dt2017_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
dt2017_bigrams_counts

# Bigram graph
dt2017_bigrams_graph <- dt2017_bigrams_counts %>%
  filter(n > 7) %>%
  graph_from_data_frame()

set.seed(2020)
g <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(dt2017_bigrams_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = g, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
```{r, results='hide'}
# For year 2018 
dt2018_bigrams <- dt2018 %>%
  unnest_tokens(bigram, wrangle.dt2018., token = "ngrams", n = 2)

# Counting the bigrams
dt2018_bigrams %>%
  count(bigram, sort = TRUE)

dt2018_bigrams_separated <- dt2018_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

dt2018_bigrams_filtered <- dt2018_bigrams_separated %>%
  filter(!word1 %in% stopwords$word) %>%
  filter(!word2 %in% stopwords$word)

dt2018_bigrams_counts <- dt2018_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
dt2018_bigrams_counts

# Bigram graph
dt2018_bigrams_graph <- dt2018_bigrams_counts %>%
  filter(n > 4) %>%
  graph_from_data_frame()

set.seed(2020)
t <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(dt2018_bigrams_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = t, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
```{r, results='hide'}
# For year 2019 
dt2019_bigrams <- dt2019 %>%
  unnest_tokens(bigram, wrangle.dt2019., token = "ngrams", n = 2)

# Counting the bigrams
dt2019_bigrams %>%
  count(bigram, sort = TRUE)

dt2019_bigrams_separated <- dt2019_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

dt2019_bigrams_filtered <- dt2019_bigrams_separated %>%
  filter(!word1 %in% stopwords$word) %>%
  filter(!word2 %in% stopwords$word)

dt2019_bigrams_counts <- dt2019_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
dt2019_bigrams_counts

# Bigram graph
dt2019_bigrams_graph <- dt2019_bigrams_counts %>%
  filter(n > 11) %>%
  graph_from_data_frame()

set.seed(2020)
t <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(dt2019_bigrams_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = t, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
```{r, results='hide'}
# For year 2020 
dt2020_bigrams <- dt2020 %>%
  unnest_tokens(bigram, wrangle.dt2020., token = "ngrams", n = 2)

# Counting the bigrams
dt2020_bigrams %>%
  count(bigram, sort = TRUE)

dt2020_bigrams_separated <- dt2020_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

dt2020_bigrams_filtered <- dt2020_bigrams_separated %>%
  filter(!word1 %in% stopwords$word) %>%
  filter(!word2 %in% stopwords$word)

dt2020_bigrams_counts <- dt2020_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
dt2020_bigrams_counts

# Bigram graph
dt2020_bigrams_graph <- dt2020_bigrams_counts %>%
  filter(n > 14) %>%
  graph_from_data_frame()

set.seed(2020)
t <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(dt2020_bigrams_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = t, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
```{r, results='hide'}
# For year 2021 
dt2021_bigrams <- dt2021 %>%
  unnest_tokens(bigram, wrangle.dt2021., token = "ngrams", n = 2)

# Counting the bigrams
dt2021_bigrams %>%
  count(bigram, sort = TRUE)

dt2021_bigrams_separated <- dt2021_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

dt2021_bigrams_filtered <- dt2021_bigrams_separated %>%
  filter(!word1 %in% stopwords$word) %>%
  filter(!word2 %in% stopwords$word)

dt2021_bigrams_counts <- dt2021_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
dt2021_bigrams_counts

# Bigram graph
dt2021_bigrams_graph <- dt2021_bigrams_counts %>%
  filter(n > 10) %>%
  graph_from_data_frame()

set.seed(2020)
t <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(dt2021_bigrams_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = t, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
```{r, results='hide'}
# For year 2022 
dt2022_bigrams <- dt2022 %>%
  unnest_tokens(bigram, wrangle.dt2022., token = "ngrams", n = 2)

# Counting the bigrams
dt2022_bigrams %>%
  count(bigram, sort = TRUE)

dt2022_bigrams_separated <- dt2022_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

dt2022_bigrams_filtered <- dt2022_bigrams_separated %>%
  filter(!word1 %in% stopwords$word) %>%
  filter(!word2 %in% stopwords$word)

dt2022_bigrams_counts <- dt2022_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
dt2022_bigrams_counts

# Bigram graph
dt2022_bigrams_graph <- dt2022_bigrams_counts %>%
  filter(n > 2) %>%
  graph_from_data_frame()

set.seed(2020)
t <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(dt2022_bigrams_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = t, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

```